A Toolbox for Manipulating and Assessing Color Palettes

### 2019-08-29 pkg/colorspace/paper/Toolbox/article.Rmd
dashed -> gray
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/colorspace@509 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

```{r hcl-palettes, echo = TRUE, eval = FALSE}
library("colorspace")
hcl_palettes(plot = TRUE)
```
```{r hcl-palettes, echo = FALSE, fig.height = 6.75, fig.width = 12, fig.cap = "Brief overview of available predefined palettes in \\pkg{colorspace}."}
library("colorspace")
hcl_palettes(plot = TRUE, mar = c(0.1, 7, 0, 0), line = 6)
```

@@

```{r hcl-palettes-sequentialm, fig.width = 8.5, fig.height = 9.0, fig.cap = "Prespecified sequential multi-hue HCL palettes available in \\code{sequential\\_hcl()} in \\pkg{colorspace}."}
hcl_palettes("sequential (multi-hue)", n = 7, plot = TRUE)
```

@@

c2 <- 10
plot(1 - i, c2 - (c2 - c1) * i, xlim = c(0, 1), ylim = c(0, 100),
  xlab = "Intensity (i)", ylab = "Coordinate", main = "Linear",
  xaxs = "i", yaxs = "i", type = "l", lwd = 2, axes = FALSE)
axis(1, at = c(0, 0.5, 1), labels = c("1", "0.5", "0"))
axis(2)
box()
lines(1 - i, c2 - (c2 - c1) * i^1.6, lwd = 2, col = gray(0.5))
mylab(0.06, c1 + 5, "c1")
mylab(0.94, c2 - 5, "c2")
mylab(0.68, 40, "p1", col = gray(0.5))
text(0.78, 40, "= 1", col = gray(0.5))
mylab(0.18, 40, "p1", col = gray(0.5))
text(0.30, 40, "= 1.6", col = gray(0.5))

@@

plot(1 - i, ci1, xlim = c(0, 1), ylim = c(0, 100),
  xlab = "Intensity (i)", ylab = "Coordinate", main = "Triangular",
  xaxs = "i", yaxs = "i", type = "l", lwd = 2, axes = FALSE)
axis(1, at = c(0, 0.5, 1), labels = c("1", "0.5", "0"))
axis(2)
box()
lines(1 - i, ci2, lwd = 2, col = gray(0.5))
mylab(0.06, c1 - 5, "c1")
mylab(1 - maxat + 0.1, cmax + 4, "cmax", ratio = 0.5)
mylab(0.94, c2 - 5, "c2")
mylab(0.77, 40, "p1", col = gray(0.5))
text(0.87, 40, "= 1", col = gray(0.5))
mylab(0.27, 40, "p1", col = gray(0.5))
text(0.39, 40, "= 1.6", col = gray(0.5))
```

@@

* Constant: `c1 = 80`.
* Linear: `c1 = 80`, `c2 = 10`, `p1 = 1` (solid) vs.\ `p1 = 1.6` (dashed).
* Triangular: `c1 = 60`, `cmax = 80`, `c2 = 10`, `p1 = 1` (solid) vs.\ `p1 = 1.6` (dashed).

>>>>

```{r hcl-palettes-0, echo = TRUE, eval = FALSE}
library("colorspace")
hcl_palettes(plot = TRUE)
```
```{r hcl-palettes, echo = FALSE, fig.height = 6.75, fig.width = 12, fig.cap = "Brief overview of available predefined palettes in \\pkg{colorspace}."}
library("colorspace")
hcl_palettes(plot = TRUE, line = 6)
```

@@

```{r hcl-palettes-sequentialm-0, echo = TRUE, eval = FALSE}
hcl_palettes("sequential (multi-hue)", n = 7, plot = TRUE)
```
```{r hcl-palettes-sequentialm, echo = FALSE, fig.width = 8.5, fig.height = 9.0, fig.cap = "Prespecified sequential multi-hue HCL palettes available in \\code{sequential\\_hcl()} in \\pkg{colorspace}."}
hcl_palettes("sequential (multi-hue)", n = 7, plot = TRUE, line = 6)
```

@@

c2 <- 10
plot(1 - i, c2 - (c2 - c1) * i, xlim = c(0, 1), ylim = c(0, 100),
  xlab = "Intensity (i)", ylab = "Coordinate", main = "Linear",
  xaxs = "i", yaxs = "i", type = "l", lwd = 2, axes = FALSE)
axis(1, at = c(0, 0.5, 1), labels = c("1", "0.5", "0"))
axis(2)
box()
lines(1 - i, c2 - (c2 - c1) * i^1.6, lwd = 2, col = gray(0.5))
mylab(0.06, c1 + 5, "c1")
mylab(0.94, c2 - 5, "c2")
mylab(0.68, 40, "p1")
text(0.78, 40, "= 1")
mylab(0.18, 40, "p1", col = gray(0.5))
text(0.30, 40, "= 1.6", col = gray(0.5))

@@

plot(1 - i, ci1, xlim = c(0, 1), ylim = c(0, 100),
  xlab = "Intensity (i)", ylab = "Coordinate", main = "Triangular",
  xaxs = "i", yaxs = "i", type = "l", lwd = 2, axes = FALSE)
axis(1, at = c(0, 0.5, 1), labels = c("1", "0.5", "0"))
axis(2)
box()
lines(1 - i, ci2, lwd = 2, col = gray(0.5))
mylab(0.06, c1 - 5, "c1")
mylab(1 - maxat + 0.1, cmax + 4, "cmax", ratio = 0.5)
mylab(0.94, c2 - 5, "c2")
mylab(0.77, 40, "p1")
text(0.87, 40, "= 1")
mylab(0.27, 40, "p1", col = gray(0.5))
text(0.39, 40, "= 1.6", col = gray(0.5))
```

@@

* Constant: `c1 = 80`.
* Linear: `c1 = 80`, `c2 = 10`, `p1 = 1` (black) vs.\ `p1 = 1.6` (gray).
* Triangular: `c1 = 60`, `cmax = 80`, `c2 = 10`, `p1 = 1` (black) vs.\ `p1 = 1.6` (gray).
